\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}
\author{Andrija Milovac, Roko Burilo}
\title{Dave The Computer Guy}
\date{23.9.2021}
\begin{document}
\maketitle
\tableofcontents
\section{Product vision}
\subsection{Simple explanation}
Dave The Computer Guy is a game whos goal is to teach you how to build a computer from scratch out of logic gates step by step.
\subsection{Story intro}
At the center of the game is fresh computer science graduate Dave.
Dave got hired at an small digital electronic components manufacturer compan called Completely-Digital.

He will work in an office with his senior hardware developer named John Dodi and their boss Dexter Crawford.

Daves day to day will consist of syncing with his boss about the work that needs to be done and doing the required work which is mostly
creating new electronic components and manufacturing them.

Whenever Dave gets stuck on a task or has no idea where to even start he can always ask John Dodi for help as he is a senior developer with 
decades of experience and wisdom.

Dave is a very motivated young person and besides working hard at his new job he decided to practice and put to use everything he learns 
at his job by building a computer at home from scratch.

The reason he wants to do this is that he was originally a software (computer science graduate) guy and only recently got into the world of hardware and he 
wishes to connect his software knowledge with his newly found hardware knowledge so that he can have a deep understanding of computers.






\section{Product market}
\section{Product implementation}
\section{Technical Details}

\end{document}